### 2019-03-12 papers/journal/problem.tex
Minor corrections

This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem to solve the existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.

@@

Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
%
The search problem is to find an assignment of variables that satisfies all the generated constraints.
%
We have used a form of this technique called satisfiability modulo theories (SMT).
%
The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc. 
%
%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
% is satisfiability of formulas with respect to some background theory.
%
Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%The existential condition search problem is represented as a bounded model checking and constraint solving. 
%
%Based upon earlier discussion, we need to answer the following search question among VTSs.
%
Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.

>>>>

This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition and performing synthesis on the incomplete VTS.

@@

Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
%
The search problem is to find an assignment of variables that satisfies all the specified constraints.
%
We have used a form of this technique called satisfiability modulo theories (SMT).
%
The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc. 
%
%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
% is satisfiability of formulas with respect to some background theory.
%
Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%The existential condition search problem is represented as a bounded model checking and constraint solving. 
%
%Based upon earlier discussion, we need to answer the following search question among VTSs.
%
Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.
